混合效应模型和计量面板数据模型的区别

### 2019-03-24 Panel-and-Mixed-Model.Rmd
fixup

---
title: "混合效应模型和计量面板数据模型的区别"
author: "Jin"
date: "2019-03"
output:
  bookdown::html_document2:
    number_sections: true
    seq_numbering: true
    fig_caption: true
    highlight: haddock
    theme: null
    md_extensions: +east_asian_line_breaks
    keep_md: true
    toc: false
    pandoc_args: ["--filter", "pandoc-crossref", "-M", "eqnPrefix="]
  bookdown::word_document2:
    fig_caption: true
    reference_docx: ./style/word-styles-02.docx
    md_extensions: +east_asian_line_breaks
    pandoc_args: ["--filter", "pandoc-crossref"]
  bookdown::pdf_document2:
    keep_tex: yes
    toc: false
    latex_engine: xelatex
    md_extensions: +east_asian_line_breaks
    pandoc_args: ["--listing", "--filter", "pandoc-crossref"]
css: ./style/markdown.css
autoEqnLabels: true
eqnPrefixTemplate: ($$i$$)
linkReferences: true
bibliography: Bibfile.bib
csl: ./style/chinese-gb7714-2005-numeric.csl
link-citations: true
---

@@

$\alpha$、$\beta$ 对所有省份在所有时间都相同。

>>>>

---
title: "混合效应模型和计量面板数据模型的区别"
author: "Jin"
date: "2019-03"
output:
  bookdown::html_document2:
    number_sections: true
    seq_numbering: true
    fig_caption: true
    highlight: haddock
    theme: null
    md_extensions: +east_asian_line_breaks
    keep_md: true
    toc: true
    pandoc_args: ["--filter", "pandoc-crossref", "-M", "eqnPrefix="]
  bookdown::word_document2:
    fig_caption: true
    reference_docx: ./style/word-styles-02.docx
    md_extensions: +east_asian_line_breaks
    pandoc_args: ["--filter", "pandoc-crossref"]
  bookdown::pdf_document2:
    keep_tex: yes
    toc: false
    latex_engine: xelatex
    md_extensions: +east_asian_line_breaks
    pandoc_args: ["--listing", "--filter", "pandoc-crossref"]
css: ./style/markdown.css
autoEqnLabels: true
eqnPrefixTemplate: ($$i$$)
linkReferences: true
bibliography: Bibfile.bib
csl: ./style/chinese-gb7714-2005-numeric.csl
link-citations: true
---

@@

$\alpha$、 $\beta$ 对所有省份在所有时间都相同。
